### 2023-08-22 resilience-safe-down.tex
up

%%%%%%%%
\subsection{Case: $\Safe=\downarrow \Safe$.}
%
%		cas unbounded counters
%

@@

Remark we did not make use of the hypothesis $\Bad$ complement of $\Safe$, simply 
$\Bad=\uparrow \Bad$ and $\Safe=\downarrow \Safe$, thus 
the above results still hold in the more general case where $\Bad$ and $\Safe$ are not complement of each others.

>>>>

%%%%%%%%
\subsection{Case: $\Safe=\downarrow \Safe$.}\label{safe-down}
%
%		cas unbounded counters
%

@@

Remark we did not make use of the
% hypothesis
property $\Bad$ complement of $\Safe$, simply 
$\Bad=\uparrow \Bad$ and $\Safe=\downarrow \Safe$, thus 
the above results still hold in the more general case where $\Bad$ and $\Safe$ are not complement of each others.

### 2023-08-22 resilience-safe-up.tex
up

\subsection{Case: $\Safe=\uparrow \Safe$.}

@@

Remark we did not make use of the hypothesis that $\Bad$ is the complement of $\Safe$, simply using
$\Bad=\downarrow \Bad$ and $\Safe=\uparrow \Safe$, thus 
the above results still hold in the more general case where $\Bad$ and $\Safe$ are not complements of each others.

>>>>

\subsection{Case: $\Safe=\uparrow \Safe$.}\label{safe-up}

@@

Remark we did not make use of the 
% hypothesis
property that $\Bad$ is the complement of $\Safe$, simply using
$\Bad=\downarrow \Bad$ and $\Safe=\uparrow \Safe$, thus 
the above results still hold in the more general case where $\Bad$ and $\Safe$ are not complements of each others.
